Dunnett's test

### 2022-08-25 text/22/dunnetts-test.Rmd
Added example to dunnetts-test.Rmd

Reject $H_0$ if $|\bar X_i-\bar X_1| \geq d(\alpha, g, n) \sqrt{2MSE/n}$

@@

>>>>

Reject $H_0$ if $\bar X_i \leq \bar X_1 - d(\alpha, g, n) \sqrt{2MSE/n}$ or $\bar X_i \geq \bar X_1 + d(\alpha, g, n) \sqrt{2MSE/n}$

@@

### Example-seed viability

In an experiment examining the effect of different disinfection protocols on orthodontic elastormeric ligatures, 120 ligatures were divided into 6 groups of 20. Each group received a different disinfection protocol, with the exception of the first group, which received no disinfection. This group served as a control group.

![](http://www.pmean.com/new-images/22/dunnetts-test-01.jpg)

Leandro Berni Osorio, Luiz Makito Osawa Gutierrez, Eduardo Martinelli de Lima, Eduardo Gonçalves Mota, and Luciane Macedo de Menezes. Disinfection of Orthodontic Elastomers and Its Effects on Tensile Strength. Turkish Journal of Orthodontics, 2021, 35(1): 22-26.

The researchers were interested in whether any of the disinfection protocols reduced the tensile strength of the ligatures. Here are the summary statistics for the maximum strength measurement.

```{r, echo=FALSE, comment=""}
mn1 <- c(21.39, 22.58, 16.94, 21.93, 19.93, 22.00)
sd1 <- c( 3.35,  2.88,  3.50,  3.05,  1.86, 3.71)
data.frame(mean=mn1, standard_deviation=sd1)
```

```{r, echo=FALSE, comment=""}
suppressMessages(suppressWarnings(library(tidyverse)))
mse <- mean(sd1^2)
d <- 2.73
n <- 20
lo <- mn1[1] - d*sqrt(2*mse/20)
hi <- mn1[1] + d*sqrt(2*mse/20)
```

lower limit = $\bar X_1$ - d(0.05, 6, 20) $\sqrt{2MSE/n}$

= `r mn1[1]` - `r d` $\sqrt{2 (`r round(mse, 2)`)/ `r n`}$

= `r round(lo, 2)`

upper limit = $\bar X_1$ + d(0.05, 6, 20) $\sqrt{2MSE/n}$

= `r mn1[1]` + `r d` $\sqrt{2 (`r round(mse, 2)`)/ `r n`}$

= `r round(hi, 2)`

You can create a simple graph from these limits.

```{r, echo=FALSE, comment=""}
data.frame(g=2:6, mn=mn1[-1]) %>%
  ggplot(aes(g, mn)) +
    geom_point() +
    geom_segment(
      x=2:6, 
      xend=2:6, 
      y=mn1[-1], 
      yend=mn1[1]) +
    geom_segment(x=1.9, y=lo, xend=6.1, yend=lo) +
    geom_segment(x=1.9, y=hi, xend=6.1, yend=hi) +
    geom_segment(x=1.9, y=mn1[1], xend=6.1, yend=mn1[1], lty="dotted") +
    expand_limits(y=c(lo, hi)) +
    expand_limits(x=c(1.5, 6.5))
```

Only the third disinfection protocol has significantly less strength compared to the control group with no disinfection.
